Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

One of the questions in the {\bf second survey}, which asked about the messaging
applications used by tertiary education teachers, opens a new line of inquiry
about what educators {\em perceive} as such, and how it is used.  Namely, the
responses indicated that teachers considered messaging application not only
traditional chats or instant messaging app such as WhatsApp or Microsoft Teams,
but also any means provided by their university for communicating with students,
such as a feature of the cmapus-wide learning management system that emails
grades to students. This suggests that teachers have a need for communication
with students, which is mostly unidirectional, and that it does not matter as
much how that need is met. However, this will need careful consideration,
including how it ties with the automation of the learning experience provided by
chatbots.

>>>>

One of the questions in the {\bf second survey}, which asked about the messaging
applications used by tertiary education teachers, opens a new line of inquiry
about what educators {\em perceive} as such, and how it is used.  Namely, the
responses indicated that teachers considered messaging applications not only
traditional chats or instant messaging apps such as WhatsApp or Microsoft Teams,
but also any means provided by their university for communicating with students,
such as a feature of the cmapus-wide learning management system that emails
grades to students. This suggests that teachers have a need for communication
with students, which is mostly unidirectional, and that it does not matter as
much how that need is met. However, this will need careful consideration,
including how it ties with the automation of the learning experience provided by
chatbots.
